Self Regulation Ontology Retest Data Report

### 2017-11-03 code/SRO_Report.Rmd
added first draft of presentation

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(lme4)
library(GGally)
library(jsonlite)
library(psych)
library(rmarkdown)
library(psych)
library(stringr)
library(plotly)
library(DT)
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}
trim <- function (x) gsub("^\\s+|\\s+$", "", x)
render_this <- function(){rmarkdown::render('SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/reports', html_notebook(toc = T, toc_float = T, code_folding = 'hide'))}
options(scipen = 1, digits = 4)
```

@@

datatable(lit_review)
```

@@

datatable(df)
```

@@

```{r warning=FALSE, message=FALSE}
rel_df %>%
  select(dv, task, spearman, pearson, icc) %>%
  gather(key, value, -dv, -task) %>%
  ggplot(aes(value, fill=task))+
  geom_histogram(alpha = 0.5, position = 'identity')+
  facet_wrap(~key)+
  theme_bw()+
  theme(legend.position = 'bottom',
        legend.title = element_blank())+
  xlab("")
```

@@

grid.arrange(p1, p2, p3, nrow=1)
```

@@

```{r warning=FALSE, message=FALSE}
measure_labels %>%
  select(dv, task, variable_type, ddm_task, num_all_trials)%>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
  filter(task == "task") %>%
  select(-var, -task) %>%
  left_join(rel_df[,c("dv", "icc")], by="dv")%>%
  # filter(ddm_task == 1) %>%
  separate(variable_type, c("overall_difference", "raw_EZ_hddm", "param"), extra="merge") %>%
  mutate(raw_EZ_hddm = ifelse(ddm_task == 0, "other", raw_EZ_hddm),
         param = ifelse(ddm_task == 0, "other", param)) %>%
  na.omit() %>%
  filter(overall_difference!='condition') %>%
  ggplot(aes(x=factor(raw_EZ_hddm, levels = c("raw", "EZ", "hddm", "other"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion", "Other")),y=icc,fill=param))+
  geom_boxplot(position = position_dodge(width=0.75))+
  facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
  theme_bw()+
  xlab("")+
  ylab("ICC")+
  theme(legend.title = element_blank())
```

>>>>

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(lme4)
library(GGally)
library(jsonlite)
library(psych)
library(rmarkdown)
library(psych)
library(stringr)
library(plotly)
library(DT)
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}
trim <- function (x) gsub("^\\s+|\\s+$", "", x)
render_this <- function(){rmarkdown::render('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/reports', html_notebook(toc = T, toc_float = T, code_folding = 'hide'))}
options(scipen = 1, digits = 4)
```

@@

lit_review
```

@@

df
```

@@

```{r warning=FALSE, message=FALSE}
rel_df %>%
  select(dv, task, spearman, pearson, icc) %>%
  gather(key, value, -dv, -task) %>%
  ggplot(aes(value, fill=task))+
  geom_histogram(alpha = 0.5, position = 'identity')+
  facet_wrap(~key)+
  theme_bw()+
  theme(legend.position = 'bottom',
        legend.title = element_blank())+
  xlab("")

ggsave('Rel_Histograms.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", limitsize = FALSE)
```

@@

grid.arrange(p1, p2, p3, nrow=1)

ggsave('Metric_Scatterplots.jpg', plot = grid.arrange(p1, p2, p3, nrow=1), device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", limitsize = FALSE)
```

@@

```{r warning=FALSE, message=FALSE}
measure_labels %>%
  select(dv, task, variable_type, ddm_task, num_all_trials)%>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
  filter(task == "task") %>%
  select(-var, -task) %>%
  left_join(rel_df[,c("dv", "icc")], by="dv")%>%
  # filter(ddm_task == 1) %>%
  separate(variable_type, c("overall_difference", "raw_EZ_hddm", "param"), extra="merge") %>%
  mutate(raw_EZ_hddm = ifelse(ddm_task == 0, "other", raw_EZ_hddm),
         param = ifelse(ddm_task == 0, "other", param)) %>%
  na.omit() %>%
  filter(overall_difference!='condition') %>%
  ggplot(aes(x=factor(raw_EZ_hddm, levels = c("raw", "EZ", "hddm", "other"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion", "Other")),y=icc,fill=param))+
  geom_boxplot(position = position_dodge(width=0.75))+
  facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
  theme_bw()+
  xlab("")+
  ylab("ICC")+
  theme(legend.title = element_blank())

ggsave('DDM_comparisons.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", limitsize = FALSE)
```
